---
title: "Test 1"
author: "Logan Niven 658775739"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 

Below, we have the code that creates the data set.

```{r echo=TRUE}
# Create website performance dataset with business terminology
webperfo <- data.frame(
  engagement = airquality$Temp,
  performance = airquality$Ozone,
  server_load = airquality$Wind
)
```

We have here the first six rows worth of data and the code that we used to show it.

```{r head}
head(webperfo)
```

With this line of code, we can get a summary of our entire data set.

```{r}
summary(webperfo)
```

With this code, we can see how many days worth of data we have.

```{r}
nrow(webperfo)
```
This is the code for finding the maximum engagement score in our data set.

```{r}
max(webperfo$engagement)
```

Here, we have the code to find the highest performance score. We had to include the "na.rm = TRUE" to exclude any missing data, which would have been recorded as the maximum.

```{r}
max(webperfo$performance, na.rm = TRUE)
```

## Question 

This chunk is used to create the plot graph seen below.

```{r}
plot(x = webperfo$engagement, y = webperfo$performance,
     main = "User Engagement vs Website Performance",
     xlab = "Daily User Engagement Score", 
     ylab = "Website Performance Score", 
    pch = 16, col = "blue")

 
    abline(lm(performance ~ engagement, data = webperfo), 
       col = "red", lwd = 2)

```

## Question 

Lastly, we have the code chunk for the correlation coefficient.

```{r}
cor(webperfo$engagement, webperfo$performance, use = "complete.obs")
```

